Cross Validation Approaches for Penalized Cox Regression

### 2019-03-06 main.tex
Edits/comments: Section 3.4

%%%%%%%%%%%%%%%%%%%%
  \subsection{Cross Validated Linear Predictors}
%%%%%%%%%%%%%%%%%%%%

@@

As in Figure~\ref{Fig:mse-brier-c}, the standard and linear predictor approaches outperform the deviance residual and $V\&VH$ approaches.  The improvement is particularly noticeable in the most difficult setting: high-dimensional data with weak signal.  Table~\ref{Tab:sim} also provides some insight into why the deviance residual and $V\&VH$ approaches perform poorly relative to standard CV and the linear predictor approach: they act conservatively, consistently choosing larger $\lam$ values and selecting fewer variables. \note{if we're going to say something about ``selecting fewer variables'', should Table 1 include the average model size?} \bnote{I'm afraid that the average model size would be confusing to the readers. The most conversative model would have the smallest model size, and would be closest to the true model size}

@@

\subsection {Cross-Validated C Index \note{Are we removing this section?}}

\par In this section, we conducted simulation experiments to compare likelihood-based cross validation against AUC-based cross validation. While the focus of this manuscript is to study valid cross-validation methods for partial-likelihood-based models such as penalized Cox rgression, the methods proposed in this paper are not applicable to some other survival machine learning models that do not involve constructing a partial likelihood. In those cases, the cross-validated C Index, also called cross-validated AUC, is one of the most popular options \citep{Subramanian2011} \citep{Simon2011a}. As is proposed by Simon et al., cross-validated AUC is computed also based on cross-validated linear predictors or some other types of prognostic factors. Thus, it is of our curiosity to see which one has a better performance when those two approaches, likelihood-based and AUC-based, are both available after we obtain the cross-validated linear predictors.

\par We conducted simulations at both low dimension (p = 50) and high dimension (p = 1000), varying the signal in the data. Results of the simulations are illustrated in Figure 5. In general, the likelihood-based approach is more stable than the AUC-based cross validation approach. For MSE ratio and Brier Score, the likelihood approach tends to select more predictive models than the AUC-based approach. For the actual $\lambda$, it is interesting that the AUC-based approach is quite liberal and selected smaller $\lambda$s, which would yield models that contain more variables.

\begin{figure}[h]
    \centering
		\includegraphics[height= 15cm ]{./figures/figure_auc.png}
    \caption{Cross-Validated AUC}
\end{figure}

%\begin{figure}[h]
%    \centering
%		\includegraphics[height= 15cm ]{./figures/figure_auc_extended.png}
%    \caption{Cross-Validated AUC}
%\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%
\subsection{Cross Validated Linear Predictors}
\label{Sec:linear-predictor}
%%%%%%%%%%%%%%%%%%%%

@@

As in Figure~\ref{Fig:mse-brier-c}, the standard and linear predictor approaches outperform the deviance residual and V\&VH approaches.  The improvement is particularly noticeable in the most difficult setting: high-dimensional data with weak signal.  Table~\ref{Tab:sim} also provides some insight into why the deviance residual and V\&VH approaches perform poorly relative to standard CV and the linear predictor approach: they act conservatively, consistently choosing larger $\lam$ values and selecting fewer variables. \note{if we're going to say something about ``selecting fewer variables'', should Table 1 include the average model size?} \bnote{I'm afraid that the average model size would be confusing to the readers. The most conversative model would have the smallest model size, and would be closest to the true model size}

@@

\subsection {Cross-Validated C Index}

\par All of the cross-validation approaches described in Section~\ref{Sec:methods} use the Cox partial likelihood, in one way or another, as the criterion upon which model selection is based.  In this section, we compare these likelihood-based approaches against an alternative approach of cross validation using concordance, also known as the cross-validated AUC (CV-AUC).  This is a widely used approach to cross-validation with time-to-event outcomes, particularly for machine learning models that are not likelihood-based \citep{Subramanian2011,Simon2011a}. This approach typically proceeds by constructing cross-validated linear predictors, as in Section~\ref{Sec:linear-predictor}, but then using those predictors to calculate concordance as opposed to partial likelihood.

\par We conducted simulations in both low dimensional ($p = 50$) and high dimensional ($p = 1000$) settings, varying the signal in the data \note{as in Section 3.1?} \note{is $n=100$ here?}. Results of the simulations are illustrated in Figure 5 \note{make this into a reference}.  We used the linear predictor approach (CV-LP) here as the representative approach for likelihood-based cross-validation.

\begin{figure}[h]
  \centering
  \includegraphics[height= 15cm ]{./figures/figure_auc.png}
  \caption{Cross-Validated AUC \note{Needs a more complete caption}}
\end{figure}

Several observations can be drawn from Figure~\ref{5}.  First, likelihood-based CV tends to select more accurate models, as judged by both mean squared error and Brier score.  Second, likelihood-based CV is also more stable than the AUC-based CV, in the sense that it tends to select a narrower range of models, with more consistent performance, than CV-AUC.  Lastly, CV-AUC is consistently more liberal than likelihood-based CV, selecting models with smaller values of the regularization parameter $\lam$, and therefore preferring models with larger coefficient values and more nonzero coefficients.
